Topic Modeling of News

### 2017-10-22 paper/R/webhoseio_explore.Rmd
process webhoseio data

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)

# Load and prepare Dataframe

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# create a character vector, with each file name represented by an entry
#june <- list.files("~/CloudStation/textmining/data/webhoseio/2017-06", pattern="*.json", full.names=TRUE) 
#july <- list.files("~/CloudStation/textmining/data/webhoseio/2017-07", pattern="*.json", full.names=TRUE) 
aug <- list.files("~/CloudStation/textmining/data/webhoseio/2017-08", pattern="*.json", full.names=TRUE) 
#sep <- list.files("~/CloudStation/textmining/data/webhoseio/2017-09", pattern="*.json", full.names=TRUE)

# a list in which each element is one of your original JSON files
#myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
myJSON <- lapply(aug, function(x) fromJSON(file=x))

length(myJSON)
```

## Convert List to Dataframe

```{r, eval=FALSE, include=FALSE}
site <- NULL
title <- NULL
text <- NULL
published <- NULL
fb_shares <- NULL
fb_likes <- NULL
section <- NULL
external_links <- NULL

for (i in 1:length(myJSON)){
  site <- append(site, myJSON[[i]]["thread"][[1]]["site"][[1]])
  title <- append(title, myJSON[[i]]["title"][[1]])
  text <- append(text, myJSON[[i]]["text"][[1]])
  published <- append(published, myJSON[[i]]["published"][[1]])

  fb_shares <- append(fb_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["shares"]])
  fb_likes <- append(fb_likes, myJSON[[i]]["thread"][[1]]["social"][[1]]["facebook"][[1]][["likes"]])

  section <- append(section, myJSON[[i]]["thread"][[1]]["section_title"][[1]])
  external_links <- append(external_links, length(myJSON[[i]]["external_links"][[1]]))

}

df <- cbind(site, title, text, published, fb_shares, fb_likes, section, external_links)
df <- data.frame(df, stringsAsFactors = FALSE)

rm(site, title, text, published, fb_shares, fb_likes, section, external_links)
```

## Define private and public service operators

```{r, eval=FALSE, include=FALSE}
private <- c("bild.de","focus.de","handelsblatt.com","spiegel.de","stern.de","welt.de","zeit.de")

df %>%
  mutate(owned = ifelse(site %in% private, "private", "public")) -> df
```

## Subset by
```{r, eval=FALSE, include=FALSE}
# .... date
df$date <- substr(df$published, 1,10)
df$date <- as.POSIXct(df$date, format ="%Y-%m-%d")

df <- subset(df, df$date > "2017-09-01")
```

```{r, eval=FALSE, include=FALSE}
# ... content
content <- c("Bundestagswahl","Merkel","Schulz","Wagenknecht","Lindner","Gauland","Özdemir",
             "CDU","SPD","FDP","AfD","Die Grünen","Die Linke")

btw <- df[which(grepl(paste(content, collapse = "|"), df$title)),]

# Save file
write.csv(btw, file="~/CloudStation/textmining/R/output/btw.csv")
```

## Load Data

```{r}
rm(list = ls())
df <- read.csv("output/btw.csv")
```

@@

```{r}
col <- brewer.pal(12, name = "Paired")

df %>%
  group_by(site) %>%
  tally(sort = TRUE) %>%
  ggplot(aes(site, n)) +
  geom_col(fill = col, alpha = .8) +
  xlab("") +
  ylab("") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Number of published Articels by Ownership

```{r}
df %>%
  group_by(owned) %>%
  tally(sort = TRUE) %>%
  ggplot(aes(owned, n)) +
  geom_col(fill = col[c(6,2)], alpha = .8) +
  geom_text(aes(label=n), position = position_stack(vjust = 0.5)) +
  xlab("") +
  ylab("") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
clean.text = function(x)
  {
  x = gsub("[[:punct:]]", " ", x)  # replace punctuation with space

  x = gsub("DIE WELT", "", x)
  x = gsub("SPIEGEL ONLINE", "", x)
  x = gsub("FOCUS Online", "", x)
  x = gsub("ZEIT ONLINE", "", x)
  x = gsub("stern de", "", x)
  x = gsub("Handelsblatt", "", x)
  x = gsub("Politik Inland Bild de", "", x)
  x = gsub("BILDplus Inhalt", "", x)
  x = gsub("Bild de", "", x)
  x = gsub("SWR Aktuell", "", x)
  x = gsub("SWR de", "", x)
  x = gsub("[ ]NDR[ ]", "", x)
  x = gsub('ZDF \"\"Morgenmagazin\"\"', "", x)
  x = gsub("ZDFmediathek", "", x)
  x = gsub("[ ]ZDF[ ]", "", x)
  x = gsub("[ ]ARD[ ]", "", x)

@@

# apply function to the "orig" dataframe
df$text_cleaned <- clean.text(df$text)

df %>%
  filter(grepl("Getty Images", text)) %>%
  select(text, text_cleaned) %>%
  htmlTable(align = "l")
```

```{r}
# get stopwords from online dict and add costum stopwords
#exceptions   <- c("nicht")
#my_stopwords <- setdiff(stopwords("german"), exceptions)
my_stopwords <- c(stopwords("german"), "spon","zeitmagazin","sz", "seitennavigation","startseite","gibt","immer","uhr","dass","mehr","sagte","sei","wurde","twitterfacebookgoogle","whatsappteilen","kartengeschichte","elbvertiefung","econa","prozent","freepik","colourbox")

# Remove stopwords
df$text_cleaned<- removeWords(df$text_cleaned, my_stopwords)

# save file
write.csv(df, file = "/Users/Franzi/CloudStation/textmining/data/news_cleaned.csv")
```

## Tokenize terms
```{r}
news.token <- df %>%
  group_by(site) %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE)  %>%
  bind_tf_idf(word, site, n) %>%
  arrange(desc(tf_idf)) 
```

# Topic Modeling
## LDA
```{r}
# Build corpus
btw.lda <- Corpus(VectorSource(df$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(btw.lda)
```

@@

k = 20 # Topics

t1 <- Sys.time()
lda20 <-LDA(dtm, 20, method="Gibbs", control=list(nstart=5, iter = 10000))
t2 <- Sys.time()
t2 - t1
```

>>>>

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

## Load Data
```{r}
rm(list = ls())
load("../output/news_cleaned.Rda")

df %>% filter(site != "zdf.de") -> df
col <- brewer.pal(12, name = "Paired")
```

## Count number of terms in a string
```{r}
df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
```

## Summary Stats
```{r}
df %>%
  group_by(site) %>%
  summarise(obs = n(),
    fb_shares.mean = mean(fb_shares),
            fb_shares.max = max(fb_shares),
            fb_likes.mean = mean(fb_likes),
            fb_likes.max = max(fb_likes),
            external_links.mean = mean(external_links),
            external_links.max = max(external_links),
            text_length.mean = mean(text_lenght),
            text_length.max = max(text_lenght))
  htmlTable(align = "l")
```

### Text Length
```{r}
ggplot(df, aes(x=as.factor(site), y=text_lenght)) +
  stat_summary(fun.y="median", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Median Text Length") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Facebook Likes
```{r}
ggplot(df, aes(x=as.factor(site), y=fb_likes)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Sum of Facebook Likes") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

```{r}
df$btw <- ifelse(grepl("Bundestagswahl", df$text, ignore.case = TRUE), 1,0)
```

@@

```{r}
ggplot(df, aes(site)) +
  geom_bar(fill="blue", alpha = .5) +
  xlab("") +
  ylab("Number of Articles") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Share of Articles mentioning Bundestagwahl
```{r}
df %>%
  group_by(site, btw) %>%
  tally() %>%
  group_by(site) %>%
  mutate(n_total = sum(n)) -> count

count %>%
  filter(btw == 1) %>%
  ggplot(aes(site, n/n_total)) +
  geom_col(fill="blue", alpha=.5) +
  xlab("") +
  ylab("Share of Articles mentioning Bundestagwahl") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

```{r}
btw <- df[which(df$btw == 1),]
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
clean.text = function(x)
  {
  x = gsub("DIE WELT", "", x)
  x = gsub("SPIEGEL ONLINE", "", x)
  x = gsub("FOCUS Online", "", x)
  x = gsub("ZEIT ONLINE", "", x)
  x = gsub("stern de", "", x)
  x = gsub("Handelsblatt", "", x)
  x = gsub("Politik Inland Bild de", "", x)
  x = gsub("BILDplus Inhalt", "", x)
  x = gsub("Bild de", "", x)
  x = gsub("SWR Aktuell", "", x)
  x = gsub("SWR de", "", x)
  x = gsub("[ ]NDR[ ]", "", x)
  x = gsub('ZDF \"\"Morgenmagazin\"\"', "", x)
  x = gsub("ZDFmediathek", "", x)
  x = gsub("[ ]ZDF[ ]", "", x)
  x = gsub("[ ]ARD[ ]", "", x)

@@

# apply function to the "orig" dataframe
btw$text_cleaned <- clean.text(btw$text)
```

## Remove Stopwords
```{r}
btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
```

## Tokenize terms
```{r}
news_words <- btw %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE)

## TF-IDF
news_words <- news_words %>%
  bind_tf_idf(word, site, n)

### Terms with high tf-idf
news_words %>%
  #filter(site == "spiegel.de") %>%
  arrange(desc(n))
```

### Add customized stopwords
```{r}
mystopwords <- c("ich","sie","passwort","uhr","bitte","videolänge","dass","mindestens","das","mail","die","zdf","schon","die","neuer abschnitt", "datenschutzerklärung","premium","nutzungsbedingungen","pflichtfelder","registrierung","anzeige","großbuchstaben","sonderzeichen","html","seitennavigation","swr","fullscreen","wochit","statista","club","sagte","mehr")

btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords)
```

## Tokenize terms
```{r}
news_words <- btw %>%
  unnest_tokens(word, text_cleaned) %>%
  count(site, word, sort = TRUE)

## TF-IDF
news_words <- news_words %>%
  bind_tf_idf(word, site, n)

### Terms with high tf-idf
news_words %>%
  #filter(site == "spiegel.de") %>%
  arrange(desc(n))
```

## Bigrams

```{r}
news_bigrams <- btw %>%
  unnest_tokens(bigram, text_cleaned, token="ngrams", n=2)

news_bigrams %>%
  count(bigram, sort = TRUE)
```

# Topic Modeling
## LDA
```{r}
# Build corpus
btw.lda <- Corpus(VectorSource(btw$text_cleaned))
# Create document-term matrix
dtm <- DocumentTermMatrix(btw.lda)

inspect(dtm)
```

@@

#Set parameters for Gibbs sampling (see https://eight2late.wordpress.com/2015/09/29/a-gentle-introduction-to-topic-modeling-using-r/)
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

k = 10 # Topics
```

```{r}
t1 <- Sys.time()
lda10 <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed=seed, best=best, burnin=burnin, iter = iter, thin=thin))
t2 <- Sys.time()
t2 - t1
```

```{r}
#write out results
lda10.topics <- as.matrix(topics(lda10))
lda10.topics
```

```{r}
#top 6 terms in each topic
lda10.terms <- as.matrix(terms(lda10,6))
```

```{r}
#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(lda10@gamma)
```

```{r}
#Find relative importance of top 2 topics
topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
```

```{r}
#Find relative importance of second and third most important topics
topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
```
